\myTitle

### 2024-06-06 tex/body-text-of-paper.tex

>>>>

We note that the RoSA markers provide the differential signal necessary to distinguish the
Feather River spring-run stock from the other CCV stocks with a predominantly fall-run
genomic background, as they do not share genome-wide ancestry with the other spring-run
stocks/lineages in the basin. In this context, it is clear that the 'fall-run' hatchery
program in the Feather River both spawns and produces many spring-run fish and RoSA heterozygotes.
Similarly, in other regions, the RoSA markers are the only way to distinguish fall-
and spring-run fish, as they otherwise share genomic background. 
In California, only the Sacramento and  Klamath basins have documented spring-run
salmon and their historical occurrence in other basins has been unclear. We find no
instance of spring-run fish in these coastal basins, but did identify one copy of the early-lineage
RoSA haplotype in the Eel River. Moreover, we identified three additional copies of a
recombinant haplotype that carries half of the RoSA SNPs from both the E and L lineages in the Eel and Russian rivers. No other clear recombinants were identified in the study populations, indicated that it arose in the California Coastal Chinook Salmon lineage, and provides further evidence of past presence of RoSA haplotypes associated with early migration.
